---
title: "Beamer Slide Template"
author: "Daniel E. Weeks"
institute: |
        | Department of Human Genetics 
        | Graduate School of Public Health
        | University of Pittsburgh
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  beamer_presentation:
     theme: "Warsaw"
     includes:
        in_header: header_pagenrs.tex
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
```

```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
library(pander)
# Set so that long lines in R will be wrapped:
opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 50)
```

Beamer R Markdown slide template
========================================================

* Easily generate Beamer slides from R Markdown.

```{r}
plot(sort(rnorm(100)))
```

Beamer R Markdown slide template
========================================================

* Notes slides can be included or excluded easily. 


\note{
\begin{center}
\textbf{NOTE}
\end{center}

This is a test note.  Toggle by altering 'setbeameroption' in header\_pagenrs.tex
}

Beamer R Markdown slide template
========================================================

The inclusion/exclusion of the notes pages is controlled by the LaTeX in the `header_pagenrs.tex` file:

* To include the notes pages, set `setbeameroption` to `show notes`
* To exclude the notes pages, set `setbeameroption` to `hide notes`